\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-06 manuscript/main.tex
modified:   manuscript/main.tex 	modified:   manuscript/our-cites.bib

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the data and summarizes the statistical evidence. Section \ref{sec:mechanism_design} presents the main result of our finding. Finally, Section \ref{sec:conclusion} concludes.

@@

In terms of real estate market, several literature has shown that several factors can influence the market pricing and strategies. The \citep{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9} documents that apart from price competition in the market, there is a lot of market inefficiency that stems from non-price competition, which suggests that as the degree of competition in the market increases, the market becomes progressively less efficient, indicating that the entry dividend begins to fall and aggregate social welfare begins to decline. Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale, while operating better compared to listing homes for sale as a broker. In addition, \citet{bailey_economic_2018} uses data from the social media site Facebook to show that social interactions can influence people's economic decisions. Their results show that people who have friends who are geographically distant in real life and who have a hunch that house prices are about to rise are more likely to buy a house than rent one. Other relevant areas of research include \citep{NIEUWERBURGH_information, salz_intermediation_2022}.

@@

\subsection{Statistical Summary}

After constructing our optimal radius, we recalcualte the number of lianjia and other brokerages' stores within this radius. To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community. We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia. Furthermore, we find that the other brokerages are also have the same tendency that they typically open stores with the same strategy as lianjia, which is consistent with our Theoretical Model's Proposition [xxxxx]. This figure is shown in Figure \ref{fig:same_distribu`tion}.
`'
\begin{table}[htb!]
    \centering
    \begin{tiny}
    \caption{Statistical Summary}
    \input{../result_tables/summary_statistics.tex}
    \label{tab:statistical}
    \end{tiny}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
    \caption{Tendency between two types of brokerages}
    \label{fig:same_distribution}
\end{figure}

\section{Theoretical Model}

@@

@@

\subsection{Stylized Fact}

@@

\subsection{Does Lianjia's Entry influence the segmented market?}

@@

\subsection{Is Lianjia's ACN strategy profitable?}

>>>>

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the data and summarizes the statistical evidence. Section \ref{sec:theoretical_model} presents a theoretical model that incoporate the analysis. Section \ref{sec:mechanism_design} presents the main result of our finding. Finally, Section \ref{sec:conclusion} concludes.

@@

In terms of real estate market, several literature has shown that several factors can influence the market pricing and strategies. The \citep{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9} documents that apart from price competition in the market, there is a lot of market inefficiency that stems from non-price competition, which suggests that as the degree of competition in the market increases, the market becomes progressively less efficient, indicating that the entry dividend begins to fall and aggregate social welfare begins to decline. Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale, while operating better compared to listing homes for sale as a broker. In addition, \citet{bailey_economic_2018} uses data from the social media site Facebook to show that social interactions can influence people's economic decisions. Their results show that people who have friends who are geographically distant in real life and who have a hunch that house prices are about to rise are more likely to buy a house than rent one. Other relevant areas of research include \citep{SIRMANS1991207, NIEUWERBURGH_information, salz_intermediation_2022}.

@@

\subsection{Statistical Summary} \label{subsec:Statistical_Summary}

After constructing our optimal radius, we recalcualte the number of lianjia and other brokerages' stores within this radius. To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community. We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia. In addition, we find that the other brokerages also have the same tendency that they typically open stores with the same strategy as Lianjia, which suggests that Lianjia does not have the market power to exclude competent companies from entering the market, and it also suggests that the market is not monopolized by Lianjia. We plot the relationship between the number of other brokerages's stores and the number of lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}.

\begin{table}[htb!]
    \centering
    \begin{tiny}
    \caption{Statistical Summary}
    \input{../result_tables/summary_statistics.tex}
    \label{tab:statistical}
    \end{tiny}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
    \caption{Tendency between two types of brokerages}
    \label{fig:same_distribution}
    Note: the x-axis is the number of lianjia's stores and the y-axis is the number of other brokerages' stores. The fit is a cubic polynomial fit.
\end{figure}

\subsection{Stylized Fact} \label{subsec:stylized_fact}

\section{Theoretical Model} \label{sec:theoretical_model}

\textbf{Should revise the model to make the model can incoporate the network effect and the platform's entry effect so that we can study that the entry of the platform can be helpful to make xxx.}

@@

The fifth proposition should be the fact that when there is negative shock to the customers, the number of transactions and the number of stores should decrease and the number of brokerage fee should decrease in the long run (which can be modeled using graph or simulation).

The sixth proposition should be the fact that before the increase of the

@@

@@

\subsection{Does Lianjia's Entry influence the segmented market?} \label{subsec:entry_effect}

@@

\subsection{Is Lianjia's ACN strategy profitable?} \label{subsec:acn_strategy}
